Journal

### 2024-10-25 Journal/notes.tex
Refactor math_commands.tex to include dsfont package for set-style numbers

$$
s^{+} = \text{min}_{m \in \NN} \left\{ m \geq s + 1 | \psi(\omega_m, \chi) \geq \rho \eta_m \right\}
$$

@@

$$
  \eta^{+} = (\rho + \lambda) \eta - \psi(\omega_m, \chi)
$$

@@

\pagebreak
\emergencystretch=2em % To account for hbox overflow warning
\printbibliography

>>>>

\begin{equation} \label{ETM-mechanism}
s^{+} = \text{min}_{m \in \NN} \left\{ m \geq s + 1 | \psi(\omega_m, \chi) \geq \rho \eta_m \right\}
\end{equation}

@@

\begin{equation} \label{eta-dyn}
  \eta^{+} = (\rho + \lambda) \eta - \psi(\omega_m, \chi)
\end{equation}

@@

\subsection*{Extension to dynamic ETM}
To further extend the problem the LMI formulation has been changed. A dynamic threshold on the ETM mechanism as been added and some matrices have been changed to account for the possible reference to include in the integrator dynamics. 
The same mechanism introduced in (\ref{ETM-mechanism}) and (\ref{eta-dyn}) has been used.

Now each layer will have its own dynamical threshold:

\begin{align*}
  \eta_i^{+} &= (\rho_{i} + \lambda_{i}) \eta_i - \psi \\
  \eta^{+} &= \bmx{
    \eta_1^{+} \\
    \vdots \\
    \eta_l^{+}
  } = \left( \bmx{
    \rho_1 & 0 & \dots & 0\\
    0 & \rho_2 & \dots & 0\\
    \vdots & \vdots & \ddots & \vdots\\
    0 & 0 & \dots & \rho_l
  } + \bmx{
    \lambda_1 & 0 & \dots & 0\\
    0 & \lambda_2 & \dots & 0\\
    \vdots & \vdots & \ddots & \vdots\\
    0 & 0 & \dots & \lambda_l
  }\right) \bmx{
    \eta_1 \\
    \vdots \\
    \eta_l
  } - \bmx{
    \psi_1 \\
    \vdots \\
    \psi_l
  } = \\
  &= \left( R + L \right) \eta - \psi
\end{align*}

I define the vector $\one \in \RR^{n_{x}} = \bmx{1 & \dots & 1}\tr$

And the Lyapunov function is now defined as $V = \tilde{x}\tr P \tilde{x} + He \left\{ \one\tr \eta \right\}$
\pagebreak
\emergencystretch=2em % To account for hbox overflow warning
\printbibliography
